Tuning complex synaptic plasticity for different timescales of memory

### 2015-11-13 Cosyne/Timecales.tex
fig captions

%\begin{SCfigure}
%\caption{The memory curve envelope. This is an upper bound on the SNR as a function of the mean recall time for any model at each individual timescale. Thus no model, no matter what its transition topology between functional states, can have a memory curve that exceeds this envelope at any given time-scale. The models that achieve this upper bound are indicated at various timescales. The number of synapses is N and the number of internal functional states of each synapse is M. }\label{fig:env}
%\includegraphics[width=0.6\linewidth]{LenvHeuristic.eps}
%\end{SCfigure}
\begin{figure}[t]
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,top},capbesidewidth=0.4\linewidth}}]{figure}{
\caption{\small{\textbf{The memory curve envelope.} This is an upper bound on the SNR as a function of the mean recall time for \textbf{\textit{any}} model at each individual timescale. Thus \textbf{\textit{no}} model, \emph{no matter what its transition topology between functional states}, can have a memory curve that exceeds this envelope at any given time-scale. The models that achieve this upper bound are indicated at various timescales. The number of synapses is $N$ and the number of internal functional states of each synapse is $M$. }}\label{fig:env}}{
\includegraphics[width=\linewidth]{LenvHeuristic.eps}}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{FitVid939.eps}
  \caption{\small{\textbf{Simulated experiment for fitting synaptic models.} Left: the matrices of transition probabilities for the true model. Right: the result of the model fitting. Top middle: the sequence of potentiation/depotentiation the synapse is subjected to and the sequence of observed synaptic weights. Middle: the true sequence of synaptic states (green line) and the model’s estimated probability distribution (heat map).}}\label{fig:fit}
\end{figure}

>>>>

%\begin{SCfigure}
%\caption{The memory curve envelope. This is an upper bound on the SNR as a function of the mean recall time for any model at each individual timescale. Thus no model, no matter what its transition topology between functional states, can have a memory curve that exceeds this envelope at any given time-scale. The models that achieve this upper bound are indicated at various timescales. The number of synapses is N and the number of internal functional states of each synapse is M. }\label{fig:env}
%\includegraphics[width=0.6\linewidth]{LenvHeuristic.eps}
%\end{SCfigure}
\begin{figure}[t]
\floatbox[{\capbeside\thisfloatsetup{capbesideposition={right,top},capbesidewidth=0.4\linewidth}}]{figure}{
\caption{\textbf{The memory curve envelope.} This is an upper bound on the SNR as a function of the mean recall time for \textbf{\textit{any}} model at each individual timescale. Thus \textbf{\textit{no}} model, \emph{no matter what its transition topology between functional states}, can have a memory curve that exceeds this envelope at any given time-scale. The models that achieve this upper bound are indicated at various timescales. The number of synapses is $N$ and the number of internal functional states of each synapse is $M$. }\label{fig:env}}{
\includegraphics[width=\linewidth]{LenvHeuristic.eps}}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{FitVid939.eps}
  \caption{\textbf{Simulated experiment for fitting synaptic models.} Left: the matrices of transition probabilities for the true model. Right: the result of the model fitting. Top middle: the sequence of potentiation/depotentiation the synapse is subjected to and the sequence of observed synaptic weights. Middle: the true sequence of synaptic states (green line) and the model’s estimated probability distribution (heat map).}\label{fig:fit}
\end{figure}
